### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@c335897429349e7d445b169fb0705b221bb98c04 🚀

We simulate traits.

@@

@@

Now that we have a metaweb\ldots..

@@

>>>>

We simulate traits. Relationship between number of traits, num output
PCA dimensions, and number of used dimensions in the model matter.
Describe how that works.

This embedding is the simplest.

@@

What does this tell us? The ensemble model is regularly the best for
ROC, but not for PR. This illustrates an inherent trade-off between
models being as ``right'' as possible versus a model being useful for
discovering false-negatives.

@@

Now that we have a metaweb, we can extend this to predict interactions
at particular places and times by decomposing the probability of
interaction at particular place and time into probability of interaction
multiplied by probability of co-occurrence via properties of conditional
probability (Gravel \emph{et al.} 2019).

How do we define? \(P(i \leftrightarrow j)\) Is it
\(P(A_{ij})P(O_{ij})\) or \(P(A_{ij})P(O_i)P(O_j)\)

@@

How do we improve out udnerstanding of this pollination network, or
determine if it is changing over time?
